---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# whisper

Simulate and visualise allele trajectories, using Wright-Fisher simulation.

## Installation

You can install the development version of whisper from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("emilmalta/whisper")
```

Load the contents into R environment using

```{r}
library(whisper)
```


## wf_sim()

The `wf_sim` function produves a vector of allele frequencies using WF simulation. By default, population size is `250`, initial allele frequency is `0.5`, and `100` generations are produced.

```{r example}
wf_sim()
```

No mutation rates or selection by default. Mutation can be simulated like so:

```{r}
wf_sim(p = 1/250, mut_to = .8, mut_from = .1)
```
Selection assumes a diploid organism, and genotype fitness is provided for each:

```{r}
# Dominant selection for A:
wf_sim(p = 1/250, fit_aa = .5)

# Additive selection for A:
wf_sim(p = 1/250, fit_Aa = .5, fit_aa = .25)
```
## wf_plot()

A ggplot of overlaid Wright-Fisher simulations can be made using `wf_plot()`:

```{r}
wf_plot(num_sims = 100)
```

Takes same parameters as the `wf_sim()` function:

```{r}
wf_plot(p = 1/250, t = 25, fit_Aa = .5, fit_aa = .25) 
```

## wf_shiny()

Currently not in this version, but there are plans for a shiny app.

